Paper Figures and Data

### 2020-08-24 Paper Figures/Paper figures Scipts.Rmd
aesthetic changes

    facet_grid(.~Species)+
    labs(fill = "Condition",y = "Aggregates per bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    guides(color = FALSE)+
    scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)))+
    scale_fill_grey()+
    theme_half_open()+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
          plot.margin = unit(c(0,.5,0,.5), "cm"),
          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=11),
          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,2,2,0),size=11),
          legend.title = element_text(size=13),legend.text = element_text(size = 11))
}
figure1F<-PlotFreqLogBin("PA14wt", "WT")
figure2F<-PlotFreqLogBin("PA14mut", "pqsL")
#####
figure1EF<-plot_grid(figure1E,figure1F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)
figure2EF<-plot_grid(figure2E,figure2F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)
```

@@

```
```{r biomass per bin}
PlotDensityLogBin<-function(strain,titulo){
  df <-hist.5.LogBinSummarize%>% filter(Strain == strain)
  ggplot()+
    geom_col(data = df, aes(x=LogBin,y=MeanBiomassLogBin*100, fill =ConditionNew),size=4,position = position_dodge( width = .9))+
    geom_errorbar(data = df,aes(x=LogBin,ymin=(MeanBiomassLogBin-SEBiomassLogBin)*100, ymax = (MeanBiomassLogBin+SEBiomassLogBin)*100, group =ConditionNew ),width = 0, size=.5,position = position_dodge(width = 1))+
    #labs(title = titulo)+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_grid(.~Species)+
    labs(fill = "Condition",y = "% biomass contribution per bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    guides(color = FALSE)+
    scale_fill_grey()+
    theme_cowplot(12)+
    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(face = "italic"))
}
PlotDensityLogBin("PA14wt", "WT")
PlotDensityLogBin("PA14mut", "pqsL")

>>>>

    facet_grid(.~Species)+
    labs(fill = "Condition",y = "Aggregates per bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    guides(color = FALSE)+
    scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)))+
    scale_fill_grey()+
    theme_half_open()+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
          plot.margin = unit(c(0,.5,0,.5), "cm"),
          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=11),
          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,2,2,0),size=11),
          legend.title = element_text(size=13),legend.text = element_text(size = 11))
}
figure1F<-PlotFreqLogBin("PA14wt", "WT")
figure2F<-PlotFreqLogBin("PA14mut", "pqsL")
#####
figure1EF<-plot_grid(figure1E,figure1F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)
figure2EF<-plot_grid(figure2E,figure2F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)

```

@@

```

```{r biomass per bin}
PlotDensityLogBin<-function(strain,titulo){
  df <-hist.5.LogBinSummarize%>% filter(Strain == strain)
  ggplot()+
    geom_col(data = df, aes(x=LogBin,y=MeanBiomassLogBin*100, fill =ConditionNew),size=4,position = position_dodge( width = .9))+
    geom_errorbar(data = df,aes(x=LogBin,ymin=(MeanBiomassLogBin-SEBiomassLogBin)*100, ymax = (MeanBiomassLogBin+SEBiomassLogBin)*100, group =ConditionNew ),width = 0, size=.5,position = position_dodge(width = 1))+
    #labs(title = titulo)+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_grid(.~Species)+
    labs(fill = "Condition",y = "% biomass contribution per bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    guides(color = FALSE)+
    scale_fill_grey()+
    theme_cowplot(12)+
    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(face = "italic"))
}
PlotDensityLogBin("PA14wt", "WT")
PlotDensityLogBin("PA14mut", "pqsL")
